Of judges, aliens and tpos

### 2020-12-29 paper/paper.tex
feat: abstract

% TODO title, "Of judges, aliens and tpos"?
\title{Total preorder in the courtroomg}
\subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
\author{
	Heltweg, Philip (3230880) \\
	University of Hagen \\
	pheltweg@gmail.com
}
\date{\today}
\maketitle

% TODO abstract
\abstract{Abstract goes here}

>>>>

% TODO title, "Total preorder in the courtroom"?
\title{Of judges, aliens and tpos}
\subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - 'Representation and processing of uncertain knowledge with logic-based methods'}
\author{
	Heltweg, Philip (3230880) \\
	University of Hagen \\
	pheltweg@gmail.com
}
\date{\today}
\maketitle

% TODO abstract
\abstract{Total preorders are a common tool to model plausibility orderings over worlds for agents in the research field of belief change. In their paper 'How to Revise a Total Preorder', Booth and Meyer present an approach to revising preorders for iterated belief revision based on assigning abstract intervals of plausibility under new evidence to worlds.

This report presents part of their work in tpo-revision operators and their properties with the help of an accompanying example and additional visualisation.}
